---
title: "20054602 432_A3"
author: "Maya Dixon"
date: "26/01/2021"
output: html_document
---

# Part 2: Visualization

## 1. Project Info

Tuesday, January 26, 2020

[Maya's Github repository link](https://github.com/maya-dixon/432)

### Load the data

```{r}
mydata <- read.csv("./FallopiaData.csv")
```

### Remove rows with "Total" with biomass < 60

```{r}
library(dplyr)

# Keeping all of the rows where their "Total" value is over 60

mydata %>% 
  group_by(Total) %>% 
  filter(Total > 60)
```

### Reorder the columns to ‘Total’, ‘Taxon’, ‘Scenario’, ‘Nutrients’, and remove the other columns

```{r}
data <- mydata %>% 
  select(Total, Taxon, Scenario, Nutrients)

# Checking to make sure the columns are in the proper order
print(data)
```

### Make a new column TotalG, which converts the ‘Total’ column from mg to grams AND replace Total with TotalG.

```{r}
data2 <- data %>% 
  mutate(TotalG = Total*0.001, .before = 1, Total = NULL)

# Check to make sure the new dataframe does not contain "Total" and has "TotalG" in it's place
print(data2)
```

### Write a custom function that will take two inputs from the user: 1. a vector of data to process (e.g. column from a data.frame object) and 2. a string that defines what calculation to perform

```{r}
myfunction <- function(x, y, ...) {

# calculating the average of the vector assigned in x
  if (y == "Average"){
  
    AVERAGE <- mean(x) 
    cat("Average =", AVERAGE )
  } 
  
#calculating the sum of the vector assigned in x
  else if (y == "Sum"){
    SUM <- sum(x)
    cat("Sum =", SUM)
  }
  
# calculating the number of rows or the number of observations of the vector assigned in x
  else if (y == "Observation"){
    OBSERVATION <- NROW(x)
    cat("Number of observations =", OBSERVATION)
  } 

# if y is anything other than "Average", "Sum" or "Observation" then the function will return an error message to the user.
  else {
    print("ERROR")
  }
}
```


#### Write some R code that uses your function to count the total number of observations in the 'Taxon' column

```{r}
myfunction(x = data2$Taxon, y = "Observation")
```

#### Write some R code that uses your function  to calculate the average TotalG for each of the two Nutrient concentrations

```{r}
myfunction(x = data2$TotalG, y = "Average")
```


### Write (i.e. save) the new data to a file called "WrangledData.csv" in the Output folder

```{r}
write.csv(data2, "~/Desktop/SCHOOL/BIOL 432/WrangledData.csv")
```






































